Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-07 paper.tex
addition to section 1

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, internet of things, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, signal-processing pipelines, and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. Additionally, interaction with real-world entities and addition of modern communication capabilities further enhance the mentioned features and give rise to a new class of systems: embedded \& cyber-physical systems (ECPS). As a consequence, reliability of ECPS becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for ECPS generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct system behavior together with the physical plant, providing compliance with target systems, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs. The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding ECPS. Reliability issues, in the development of ECPS, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with a high degree of reliability, according to their original design and requirements ({\it e.g.}, real-time)~\cite{Kopetz11}. They are ubiquitous in modern day information systems and are also becoming increasingly important in our society, due to their use to process, monitor, control, and even replace every human activity: factories, power plants, mobile devices, robotics, traffic control, vehicles, and home appliances~\cite{xu15}. Besides, they are also used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers.

@@

Besides, when physical interaction with the real world is needed, which happens in ECPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, such models can be used to synthesize a given particular system, by ensuring that all needed functions are correctly implemented and the correct behavior is exhibited, {\it i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

For instance, one may argue that a Linux device driver \cite{ldd} was verified and correctly uses the related kernel services; however, not much can be said about correct access to the associated hardware and its use, {\it i.e.}, if \textit{read} and \textit{write} operations are performed according to what is specified in the device's datasheet and setup periods are respected, for instance. In summary, the main goal would be to ensure that the developed driver is compliant with the underlying hardware, which goes further than code correctness and also tackles interaction with surrounding entities.

@@

A number of distinctive characteristics might influence the ECPS verification and synthesis process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency)~\cite{Kroening15} or even new structures provided with the goal of ensuring more computational capacity~\cite{cudalucas} must be considered during verification. Such observations expand the addressed issues and even complement what was mentioned previously.

The goals of the present article is to briefly present part of the established research and also clarify current trends, which are mainly driven by ECPSs, IoT, and ML. We present a brief discussion about models for ECPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, Craig interpolants, counterexample guided inductive synthesis, and system model incorporation, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section~\ref{achievements} then describes current achievements and future trends in verification and synthesis of ECPS and Section \ref{Newapp} addresses new applications, which take into account the new trends ({\it e.g.}, ML) mentioned here. Finally, we conclude and describe future work in Section~\ref{conclusions}.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, internet of things, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, signal-processing pipelines, and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. Additionally, interaction with real-world entities and addition of modern communication capabilities further enhance the mentioned features and give rise to a new class of systems: embedded \& cyber-physical systems (ECPS). As a consequence, reliability of ECPS becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for ECPS generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct system behavior together with physical plants, providing compliance with target systems, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs. The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding ECPS. Reliability issues, in the development of ECPS, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with high degree of reliability, according to their original design and requirements ({\it e.g.}, real-time)~\cite{Kopetz11}. They are ubiquitous in modern day information systems and are also becoming increasingly important in our society, due to their use to process, monitor, control, and even replace every human activity: factories, power plants, mobile devices, robotics, traffic control, vehicles, and home duties~\cite{xu15}. Besides, they are also used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers.

@@

Besides, when physical interaction with the real world is needed, which happens in ECPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, such models can be used to evaluate and even synthesize a given particular system, by ensuring that all needed functions are correctly implemented and the correct behavior is exhibited, {\it i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

For instance, one may argue that a Linux device driver \cite{ldd} was verified and correctly uses the related kernel services ({\it e.g.,} exported symbols and scheduling); however, not much can be said about correct access to the associated hardware and its use, {\it i.e.}, if \textit{read} and \textit{write} operations are performed according to what is specified in the device's datasheet and setup periods are respected, for instance. In summary, the main goal would be to ensure that the developed driver is compliant with the underlying hardware, which goes further than code correctness and also tackles interaction with surrounding entities.

@@

A number of distinctive characteristics might influence the ECPS verification and synthesis process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency)~\cite{Kroening15} or even new structures provided with the goal of ensuring more computational capacity~\cite{cudalucas} must be considered during verification. Such observations expand the addressed issues and even complement what was previously mentioned.

The goals of the present article is to briefly present part of the established research and also clarify current trends, which are mainly driven by ECPSs, IoT, and ML. We present a brief discussion about models for ECPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, Craig interpolants, counterexample guided inductive synthesis, and system model incorporation, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section~\ref{achievements} then describes current achievements and future trends in verification and synthesis of ECPS and Section \ref{Newapp} addresses new applications, which take into account the new trends ({\it e.g.}, ML) mentioned here. Finally, we conclude and describe future work, in Section~\ref{conclusions}.
